\documentclass[a4paper,10pt,oneside]{scrreprt}
\usepackage[latin1]{inputenc}
\usepackage[english]{babel}
\usepackage{graphicx}
\usepackage{float}
\usepackage{geometry}
\geometry{verbose,a4paper,tmargin=15mm,bmargin=25mm,lmargin=15mm,rmargin=15mm}
\usepackage{paralist}

\usepackage{paracol}

\usepackage{todonotes}

\usepackage{listings}
\lstset{language=Java,
	tabsize=2,
	showspaces=false,
	showtabs=false,
	breaklines=true,
	showstringspaces=false,
	breakatwhitespace=true,
	commentstyle=\color{pgreen},
	keywordstyle=\color{pblue},
	stringstyle=\color{pred},
	basicstyle=\footnotesize\ttfamily,
	moredelim=[il][\textcolor{pgrey}]{$$},
	moredelim=[is][\textcolor{pgrey}]{\%\%}{\%\%}
}

\usepackage{tikz}
\usetikzlibrary{calc,patterns,angles,quotes}

\usepackage{caption}
\usepackage{subcaption}
\usepackage{tabularx} % in the preamble

\usepackage{pdfpages}

%\usepackage{indentfirst} % for always indenting the first paragraphs

\usepackage{wrapfig}
\usepackage{lipsum}
\usepackage[linewidth=1.2pt,linecolor=red]{mdframed} % for boxes around wrapfigure and text

\begin{document}


\begin{center}
	Submitted by Group 18

	\bigskip

	\begin{tabular}{c}
	Group Members: \\
	CETIN, Ulfet (391819); GRUCZKA, FILIP (413279);	LIPINSKI, Bartosz (413177) \\
	SZYMANSKI, Bartosz (411949); GONG, Zeheng (378125)\\
	\end{tabular}

	\bigskip

	DIS1 WS 19/20 - Project Milestone V\\
	Evaluation of Low-Fidelity Prototypes\\

	%	(ordered on lastname basis)
\end{center}
\vspace{-1cm}

\clearpage

\begingroup
\let\clearpage\relax
	\chapter{Study protocol of the evaluation}
\endgroup


\section{Objective of the study}
Objective of our study is to discover which of our solutions is the best and choose this one base on observations of potential users. We want to get their impression if they find solution helpful, if they would like to use them and if they will not have any problems using it. In our evaluation will help prototypes, which will give users sense of using a real device.



\section{Contextual Information}
We will make an appointment in building of Computer Science Faculty, to make user feel at least a little bit like in a crowded shop mall. In two evaluations we will pretend situation like in supermarket, with choosing products and scanning them. 


\section{Details of the task}
In the second solution we will use Model Extraction. Interviewer will give user carboards with prototypes of screens of application. User's goal will be to describe what he sees, what are his impressions and if he finds the prototype intuitive. Thanks to this, we can check if our vision of application is clear and understandable for people not involved in creation of it.

\section{Experimental Procedure}
				
\section{Roles of Team Members(Optional)}

\section{Photo of setup(Optional)}

\section{STN for prototypes(Optional)}

\begingroup
\let\clearpage\relax
	\chapter{Evaluation with the user}
\endgroup

\section{Solution \#1}
\subsection{Unedited video}

\subsection{Notes collected during evaluation(optional)}

\subsection{Important findings}

\section{Solution \#2}
\subsection{Unedited video}

\subsection{Notes collected during evaluation(optional)}

\subsection{Important findings}

\section{Solution \#3}
\subsection{Unedited video}

\subsection{Notes collected during evaluation(optional)}

\subsection{Important findings}

\end{document}}
