\begingroup
\let\clearpage\relax
	\chapter{Study protocol of the evaluation}
\endgroup


\section{Objective of the study}
Objective of our study is to discover which of our solutions is the best and choose this one base on observations of potential users. We want to get their impression if they find solution helpful and especially fun. If they would like to use them and if they will not have any problems with usage. In our evaluation will help prototypes, which will give users sense of using a real device.



\section{Contextual Information}
We will make an appointment in building of Computer Science Faculty, to make user feel at least a little bit like in a crowded shop mall. In two evaluations we will pretend situation like in supermarket, with choosing products and scanning them. 


\section{Details of the task}
In the second solution we will use Model Extraction. Interviewer will give user carboards with prototypes of screens of application. User's goal will be to describe what he sees, what are his impressions and if he finds the prototype intuitive. Thanks to this, we can check if our vision of application is clear and understandable for people not involved in creation of it.

\section{Experimental Procedure}
Each of the user will follow the same path of the experiment. Before evaluation users will have no idea about out solutions. Before experiments will starts ...

\section{Roles of Team Members(Optional)}

\section{Photo of setup(Optional)}

\section{STN for prototypes(Optional)}

\begingroup
\let\clearpage\relax
	\chapter{Evaluation with the user}
\endgroup

\section{Solution \#1}
\subsection{Unedited video}

\subsection{Notes collected during evaluation(optional)}

\subsection{Important findings}
- Both of the users were strugeling with "shopping bag" icon on one of the pages. One of the user was thinking that's kind of security button. After explanation to them, thay have found improvement - change icon to "a shopping trolley", which will be obvious.\\
- Users had problems to discover how to choose country. Our idea was to imitate "Google Earth", but that was not as obvious for our users. \\
- Both users got stuck on "items" page. They mentioned that we already displayed items on one screen before. Our solution should include explicit information, about each subpages. In this case your personal shopping list page.\\
-Female user liked our solution - she find it very interesting to extend doing a regular shoping to something more interactive and unusual. She said that our solution stands out for people who likes to meet new cultures and facts.
